---
title: "Alcohol vs Seat choice"
author: "David Barton"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The middle has the most people sitting there compared to the front and back, with 89. The Back has the least with 36, and the front is in the middle with 40. The seating in the back is the highest with 12.580471, the middle has 6.225381, and the front in last with 3.806013.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

It is interesting to see the P-Value this small at 0.000116. That means something different is happening statistically between the values.  

```{r}
plot(TukeyHSD(model1))
```

After looking at the 95% confindence level. It's clear the confidence intervals of the front, back, and middle seats. It has 0 showing the lines are different or they aren't. I saw that the front-back and middle back are different, because 0 does not go through it; but, for the middle front seats, 0 goes through the confidence interval making it clear there is nothing different.   

## Conclusions


